The Tor Network - Design and Defenses \\ \Large Computer Security 1 - CS5460 \\ \LaTeX{}

### 2013-12-10 paper.tex
minor fixes

\documentclass[journal]{IEEEtran}
\usepackage{graphicx,mathtools}

@@

\begin{figure}[htbp]
\centering
\begin{minipage}{8 cm}
    \includegraphics[width=80mm]{resources/circuit-building-1.png}
    \caption{The user's software first downloads a directory list of Tor relays. This information is later used to construct a circuit through the network.\cite{McCoy2008}\cite{TorOverview}}
\end{minipage}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\begin{minipage}{8 cm}
    \includegraphics[width=80mm]{resources/circuit-building-2.png}
    \caption{A Tor circuit is incrementally constructed using layers of encryption. Each node has limited visibility, and no individual node knows the whole circuit.\cite{TorOverview}}
\end{minipage}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\begin{minipage}{8 cm}
    \includegraphics[width=80mm]{resources/circuit-construction.png}
    \caption{A Tor circuit is incrementally constructed using layers of encryption. Each node has limited visibility, and no individual node knows the whole circuit.\cite{TorOverview}}
\end{minipage}
\end{figure}

@@

One of the most famous examples of Internet censorship is the Great Firewall of China, a project launched in late 2003 which aims to prohibit individuals from using the Internet for activities which are not approved by the Chinese government. The Chinese Ministry of Public Security maintains the most sophisticated content-filtering regime in the world and actively engages in DNS cache poisoning, IP/URL blocking, and packet filtering.

@@

% https://www.torproject.org/about/overview.html.en
\bibitem{TorOverview}
  Overview of Tor

>>>>

\documentclass[journal]{IEEEtran}
\usepackage{graphicx,mathtools}
\usepackage[T1]{fontenc}

@@

\begin{figure}[htbp]
\centering
\begin{minipage}{8 cm}
    \includegraphics[width=80mm]{resources/circuit-building-1.png}
    \caption{The user's software first downloads a directory list of Tor relays. This information is later used to construct a circuit through the network.\cite{McCoy2008}}
\end{minipage}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\begin{minipage}{8 cm}
    \includegraphics[width=80mm]{resources/circuit-building-2.png}
    \caption{A Tor circuit is incrementally constructed using layers of encryption. Each node has limited visibility, and no individual node knows the whole circuit.}
\end{minipage}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\begin{minipage}{8 cm}
    \includegraphics[width=80mm]{resources/circuit-construction.png}
    \caption{Construction of a Tor circuit.}
\end{minipage}
\end{figure}

@@

One of the most famous examples of Internet censorship is the Great Firewall of China, a project launched in late 2003 which aims to prohibit individuals from using the Internet for activities that are not approved by the Chinese government. The Chinese Ministry of Public Security maintains the most sophisticated content-filtering regime in the world and actively engages in DNS cache poisoning, IP/URL blocking, and packet filtering.

@@
